# Simple diagrams examples {#examples}

Since this project is focused on embedding diagrams textual descriptions into R Markdown,
let's start with few examples just to illustrate a principle.

> BTW: there is a lot of drawings types that you can get from R Markdown alone, by using R packages
> or Python's matplot lib for example. You may want to check this out too [TODO: references](TODO).

## Example with inline diagram description {#examples-inline}

This example shows how to embed diagrams, describing them right in `.Rmd` file

This code:

````R
`r ''````{r echo=FALSE, results='asis'}
  to_diagram("graphviz", "Hello World",
  "digraph G {Hello->World}"
  )
```
````

would produce following diagram:

```{r echo=FALSE, results='asis'}
  to_diagram("graphviz", "Hello World",
  "digraph G {Hello->World}"
  )
```

\newpage

## Example with diagram data from file {#examples-fromFile}

This example shows how to embed diagrams with data from outer files.

This code:

`````R
`r ''````{r echo=FALSE, results='asis'}
  to_diagram("erd", "Entity Relation", src="../diagrams/examples/project.erd")
```
`````

would produce following diagram:

``` {r echo=FALSE, results='asis'}
  to_diagram("erd", "Entity Relation", src="../diagrams/examples/project.erd")
```

---

File **diagrams/examples/project.erd** content:
```{r echo=FALSE, comment=''}
cat(readLines("../diagrams/examples/project.erd"), sep = "\n")
```

##

More examples for your inspiration can be found in [this section](#examples-kroki).

Details about embedding diagrams is [here](#usage)
