```{r, include=FALSE}
source("../_fun.R", local = knitr::knit_global())
```

# Simple diagrams examples {#examples}

Since this project is focused on embedding diagrams textual descriptions into **R Markdown**,
let's start with few examples just to illustrate a principle.

> BTW: there is a lot of drawings types that you can get from **R Markdown** alone, by using **R** packages
> or Python's matplot lib for example. You may want to check this out too<!-- [TODO: references](TODO) -->.

### Example with inline diagram description {- #examples-inline}

This example shows how to embed diagrams, describing them right in the `.Rmd` files.

````R
`r ''````{r, hello-world, dia="graphviz", fig.cap="Hello World"}
  to_diagram("digraph G {Hello->World}")
```
````

```{r, hello-world, dia="graphviz", fig.cap="Hello World", out.height=if (knitr::is_latex_output()) "4cm" else ""}
  to_diagram("digraph G {Hello->World}")
```

\newpage

### Example with diagram data from file {- #examples-fromFile}

This example shows how to embed diagrams with data from outer files.

<!-- TODO: use tidy for code blocks -->

\small

`````R
`r ''````{r, examples-entity-relation, dia="erd", fig.cap="Entity Relation"}
  to_diagram(src="../diagrams/examples/project.erd")
```
`````

\normalsize

```{r, examples-entity-relation, dia="erd", fig.cap="Entity Relation", out.width=if (knitr::is_latex_output()) "8cm" else ""}
  to_diagram(src="../diagrams/examples/project.erd")
```

<!-- Since there is no pages on HTML output - put a dashline -->

```{r echo=FALSE, results='asis', eval=knitr::is_html_output()}
cat("---")
```

\newpage


File **diagrams/examples/project.erd** content:
```{r echo=FALSE, comment=''}
cat(readLines("../diagrams/examples/project.erd"), sep = "\n")
```

### More examples {- #examples-more}

More examples for your inspiration can be found in [this section](#examples-kroki).

Details about embedding diagrams is [here](#usage)
