# Kroki usage examples {#examples-kroki}

I've omitted some examples from [Kroki](https://kroki.io/examples.html) and left only those
that are most useful in a daily life of most developers (IMO).

If you check docs for [supported diagrams renderers](https://kroki.io/#support) then you'll find for sure
a few more interesting usecases.

All diagrams data for examples of this section resides in [docs_src/diagrams/examples](https://github.com/Godhart/devdoc-swissknife/tree/main/docs_src/diagrams/examples) dir of this repo.
Each diagram is included into doc by adding following code section into document file:

````R
`r ''````{r, <reference-label>, dia="from_src", fig.cap="<Caption for your figure>"}
  to_diagram(src="../diagrams/<src_file_path_within_diagrams_dir>")
```
````

Full code for this whole section is [here](https://github.com/Godhart/devdoc-swissknife/blob/main/docs_src/devdoc-swissknife-en/03-KrokiExamples.Rmd)

This usage pattern is described in the following section [TODO](#TODO)

\newpage

## C4 Context Diagram (PlantUML+C4) {#kroki-c4context}

Engine: `c4plantuml`

```{r, examples-c4context, dia="from_src", fig.cap="Example - C4 Context Diagram", out.height = if(knitr::is_latex_output()) "15cm" else ""}
  to_diagram(src="../diagrams/examples/c4plantuml-context.Rmd",
             dformat=if(knitr::is_html_output()) "" else "png") # Text is not scaled as intended when converted to PDF so use PNG
```

```{r echo=FALSE, results='asis', eval=knitr::is_latex_output()}
cat("> *NOTE: inserted as PNG image due to errors in SVG to PDF conversion")
```

\newpage

## C4 Container Diagram (PlantUML+C4) {#kroki-c4container}

Engine: `c4plantuml`

```{r, examples-c4container, dia="from_src", fig.cap="Example - C4 Container Diagram"}
  to_diagram(src="../diagrams/examples/c4plantuml-container.Rmd",
             dformat=if(knitr::is_html_output()) "" else "png") # Text is not scaled as intended when converted to PDF so use PNG
```

```{r echo=FALSE, results='asis', eval=knitr::is_latex_output()}
cat("> *NOTE: inserted as PNG image due to errors in SVG to PDF conversion")
```

\newpage

## C4 Component Diagram (PlantUML+C4) {#kroki-c4component}

Engine: `c4plantuml`

```{r, examples-c4component, dia="from_src", fig.cap="Example - C4 Component Diagram", out.height = if(knitr::is_latex_output()) "15cm" else ""}
  to_diagram(src="../diagrams/examples/c4plantuml-component.Rmd",
             dformat=if(knitr::is_html_output()) "" else "png") # Text is not scaled as intended when converted to PDF so use PNG
```

```{r echo=FALSE, results='asis', eval=knitr::is_latex_output()}
cat("> *NOTE: inserted as PNG image due to errors in SVG to PDF conversion")
```

\newpage

## Block Diagram {#kroki-blockdiag}

Engine: `blockdiag`

```{r, examples-blockdiag, dia="from_src", fig.cap="Example - Block Diagram"}
  to_diagram(src="../diagrams/examples/blockdiag.Rmd")
```

\newpage

## Digital Timing Diagram {#kroki-timing}

Engine: `wavedrom`

```{r, examples-timing, dia="from_src", fig.cap="Example - Digital Timing Diagram"}
  to_diagram(src="../diagrams/examples/wavedrom.Rmd")
```

\newpage

## Bytefield {#kroki-bytefield}

Engine: `bytefield`

```{r, examples-bytefield, dia="from_src", fig.cap="Example - Bytefield"}
  to_diagram(src="../diagrams/examples/bytefield.Rmd")
```

\newpage

## Packet Diagram {#kroki-packet}

Engine: `packetdiag`

```{r, examples-packet, dia="from_src", fig.cap="Example - Packet Diagram"}
  to_diagram(src="../diagrams/examples/packetdiag.Rmd")
```

\newpage

## Sequence Diagram #1 (PlantUML) {#kroki-pumlSequence}

Engine: `plantuml`

```{r, examples-pumlSequence, dia="from_src", fig.cap="Example - Sequence Diagram - PlantUML", out.height = if(knitr::is_latex_output()) "15cm" else ""}
  to_diagram(src="../diagrams/examples/plantuml-seqdiag.Rmd")
```

\newpage

## Sequence Diagram #2 (SeqDiag) {#kroki-sequence}

Engine: `seqdiag`

```{r, examples-sequence, dia="from_src", fig.cap="Example - Sequence Diagram - SeqDiag"}
  to_diagram(src="../diagrams/examples/seqdiag.Rmd")
```

\newpage

## Commit Graph {#kroki-commitgraph}

Engine: `pikchr`

> *NOTE: pikchr is giving troubles in PDF/PNG (produced SVG output is only web-browser friendly)*\
> *That's why this diagram is absent in PDF version*

```{r, examples-commitgraph, dia="from_src", fig.cap="Example - Commit Graph", eval=knitr::is_html_output()}
  to_diagram(src="../diagrams/examples/pikchr-commit-graph.Rmd")
```

\newpage

## Use Case Diagram {#kroki-pumlUsecase}

Engine: `plantuml`

```{r, examples-pumlUsecase, dia="from_src", fig.cap="Example Block Diagram"}
  to_diagram(src="../diagrams/examples/plantuml-usecase.Rmd")
```

\newpage

## Mind Map {#kroki-pumlMindmap}

Engine: `plantuml`

```{r, examples-pumlMindmap, dia="from_src", fig.cap="Example - Mind Map"}
  to_diagram(src="../diagrams/examples/plantuml-mindmap.Rmd")
```

\newpage

## PlantUML (More examples) {#kroki-pumlMore}

PlantUML supports more diagram types like timing diagram, gantt and many more.

You can use any of them just like in previous examples.

Check PlantUML docs [https://plantuml.com/](https://plantuml.com/) for filling in diagram data.

\newpage

## Gantt {#kroki-gantt}

Engine: `mermaid`

> *NOTE: mermaid is giving troubles in PDF/PNG (produced SVG output is only web-browser friendly)*
> *That's why this diagram is absent in PDF version*

```{r, examples-gantt, dia="from_src", fig.cap="Example - Gantt", eval=knitr::is_html_output()}
  to_diagram(src="../diagrams/examples/mermaid-gantt.Rmd")
```
