# Simple diagrams examples

Since this project is focused on embedding diagrams text descriptions into R Markdown
let's start with few examples just to illustrate a principle.

## Example with inline diagram description

This example shows how to embed diagrams, describing them right in Rmd file

This code:

````R
`r ''````{r echo=FALSE, results='asis'}
  to_diagram("graphviz", "Hello World",
  "digraph G {Hello->World}"
  )
```
````

would produce following diagram:

```{r echo=FALSE, results='asis'}
  to_diagram("graphviz", "Hello World",
  "digraph G {Hello->World}"
  )
```

> *Take a NOTE: When diagrams are inserted like this it's **IMPORTANT** that <Drawing name>
> ("Hello World" in this example) is **UNIQUE** for **WHOLE** doc.*\
> More details on usage is in [...](TODO:)

\newpage

## Example with diagram data from file

This example shows how to embed diagrams with data from outer files.

This code:

`````R
`r ''````{r echo=FALSE, results='asis'}
  to_diagram("erd", "Entity Relation", src="diagrams/examples/project.erd")
```
`````

would produce following diagram:

``` {r echo=FALSE, results='asis'}
  to_diagram("erd", "Entity Relation", src="diagrams/examples/project.erd")
```

---

File **diagrams/examples/project.erd** content:
```{r echo=FALSE, comment=''}
cat(readLines('diagrams/examples/project.erd'), sep = '\n')
```

## More examples

More examples can be found in [this section](#examplesKroki).
