# Simple diagrams examples

Since this project is focused on embedding diagrams into Rmarkdown
let's start with few examples just to illustrate principle.

## Example with inline diagram description

This example shows how to embed diagrams, describing them right in Rmd file

This code:

````R
`r ''````{r echo=FALSE, results='asis'}
  to_diagram("graphviz", "Hello World",
  "digraph G {Hello->World}"
  )
```
````

would produce following diagram:

```{r echo=FALSE, results='asis'}
  to_diagram("graphviz", "Hello World",
  "digraph G {Hello->World}"
  )
```

\newpage

## Example with diagram data from file

This example shows how to embed diagrams with data from outer files

This code:

`````R
`r ''````{r echo=FALSE, results='asis'}
  to_diagram("erd", "Entity Relation", src="diagrams/project.erd")
```
`````

would produce following diagram:

``` {r echo=FALSE, results='asis'}
  to_diagram("erd", "Entity Relation", src="diagrams/project.erd")
```

---

File **diagrams/project.erd** content:
```{r echo=FALSE, comment=''}
cat(readLines('diagrams/project.erd'), sep = '\n')
```
