# Kroki usage examples

I've ommited some examples from [Kroki!](https://kroki.io/examples.html) and left only those
that are realy useful in daily life of most developrs (IMHO).

All diagrams data for examples of this section resides in `docs_src/diagrams` dir of this repo.
Each diagram is included into doc by adding following code section into document file:

````R
`r ''````{r echo=FALSE, results='asis'}
  to_diagram("from_src", "<Drawing name>", src="diagrams/<src_file_name>")
```
````

> *it's **IMPORTANT** that <Drawing name> is **UNIQUE** for **WHOLE** doc.*

This usage pattern is described in the following section [TODO](#TODO)

\newpage

## C4 Context Diagram (PlantUML+C4)

Engine: `c4plantuml`

```{r echo=FALSE, results='asis'}
  to_diagram("from_src", "Example - C4 Context Diagram", src="diagrams/examples/c4plantuml-context.Rmd")
```

\newpage

## C4 Container Diagram (PlantUML+C4)

Engine: `c4plantuml`

```{r echo=FALSE, results='asis', eval=knitr::is_html_output()}
cat("> *NOTE: inserted as SVG image so text on image is not searchable.\\\nCan't insert inline due to large horizontal size*")
```

```{r echo=FALSE, results='asis'}
  to_diagram("from_src", "Example - C4 Container Diagram", inline=FALSE, src="diagrams/examples/c4plantuml-container.Rmd")
```

\newpage

## C4 Component Diagram (PlantUML+C4)

Engine: `c4plantuml`

```{r echo=FALSE, results='asis'}
  to_diagram("from_src", "Example - C4 Component Diagram", src="diagrams/examples/c4plantuml-component.Rmd")
```

\newpage

## Block Diagram

Engine: `blockdiag`

```{r echo=FALSE, results='asis'}
  to_diagram("from_src", "Example - Block Diagram", src="diagrams/examples/blockdiag.Rmd")
```

\newpage

## Digital Timing Diagram

Engine: `wavedrom`

```{r echo=FALSE, results='asis'}
  to_diagram("from_src", "Example - Digital Timing Diagram", src="diagrams/examples/wavedrom.Rmd")
```

\newpage

## Bytefield

Engine: `bytefield`

```{r echo=FALSE, results='asis'}
  to_diagram("from_src", "Example - Bytefield", src="diagrams/examples/bytefield.Rmd")
```

\newpage

## Packet Diagram

Engine: `packetdiag`

```{r echo=FALSE, results='asis', eval=knitr::is_html_output()}
cat("> *NOTE: inserted as SVG image so text on image is not searchable.\\\nCan't insert inline due to large horizontal size*")
```

```{r echo=FALSE, results='asis'}
  to_diagram("from_src", "Example - Packet Diagram", inline=FALSE, src="diagrams/examples/packetdiag.Rmd")
```

\newpage

## Sequence Diagram #1 (PlantUML)

Engine: `plantuml`

```{r echo=FALSE, results='asis'}
  to_diagram("from_src", "Example - Sequence Diagram - PlantUML", src="diagrams/examples/plantuml-seqdiag.Rmd")
```

\newpage

## Sequence Diagram #2 (SeqDiag)

Engine: `seqdiag`

```{r echo=FALSE, results='asis'}
  to_diagram("from_src", "Example - Sequence Diagram - SeqDiag", src="diagrams/examples/seqdiag.Rmd")
```

\newpage

## Commit Graph

Engine: `pikchr`

```{r echo=FALSE, results='asis', eval=knitr::is_html_output()}
  to_diagram("from_src", "Example - Commit Graph", src="diagrams/examples/pikchr-commit-graph.Rmd")
```

\newpage

## Use Case Diagram

Engine: `plantuml`

```{r echo=FALSE, results='asis'}
  to_diagram("from_src", "Example Block Diagram", src="diagrams/examples/plantuml-usecase.Rmd")
```

\newpage

## Mind Map

Engine: `plantuml`

```{r echo=FALSE, results='asis'}
  to_diagram("from_src", "Example - Mind Map", src="diagrams/examples/plantuml-mindmap.Rmd")
```

\newpage

## PlantUML (More examples)

PlantUML supports more diagram types like timing diagram, gantt and many more.

You can use any of them just like in previous examples.

Check PlantUML docs [https://plantuml.com/](https://plantuml.com/) for filling in diagram data.

\newpage

## Gantt

Engine: `mermaid`

> *NOTE: mermaid is giving troubles in PDF (looks like transparency issues)*

```{r echo=FALSE, results='asis'}
  to_diagram("from_src", "Example - Gantt", src="diagrams/examples/mermaid-gantt.Rmd")
```
